%!TEX root = ../main.tex
Throughout this report has been described the creation of a system for gathering and monitoring data from the SDU go-kart.
Here will be presented a consollidation of the outcome of the different parts of the project, as well as some of the observations with respect to the working methods employed by the authors.
\\~\\
Initially, an attempt was made to exemplify the requirements of a system such as the one being developed.
Each part of the system was analysed to this effect.
While the analysis does touch on every part of the project, it was not until late in the project that the value of the analysis was clear to the authors.
Some mistakes were made to this effect. 
For instance, on making the connection between the PC and the Zybo, three different methods were tried before finally settling on socat.
A process that might have been avoided with proper analysis of the problem at hand.
Even with the detours, a collection of requirements were set.
Many of which were verified in part \ref{part:verification}.

\section{State of the Requirements}
The results of the verification is consolidated here to provide an overview of the state of the project.
Each requirement is listed with an explanation as to whether the requirement was met.
Requirements marked with \cmark were fully realised, -- partially and \xmark ~are not realised.

\subsection{Functional Requirements}
\begin{itemize}
	\item[\cmark] \textbf{Read data from sensors/data producers:}
	Data was successfully read from a GPS module.
	The data was gathered using the real GPS module but service virtualisation was utilised in verifying the functionality of the node responsible of handling the GPS.
	This is explained in section \ref{sec:node_software}.
	\item[\cmark] \textbf{Timestamp all data:}
	A system was devised such that a packet contain the tinestamp of the data is sent prior to sending the data.
	The timestamp was left out of the actual data packet to limit the bandwidth spent on transmitting timestamps.
	This is explained in section \ref{sec:node_software}.
	\item[\cmark] \textbf{Transmit data wirelessly between Zybo and monitoring station:}
	This was succesfully done using a WiFi connection.
	An ad-hoc network was created using a WiFi/USB dongle, which is connected to from a PC.
	Verification of this feature can be seen in section \ref{sec:wifiverification}.
	\item[\xmark] \textbf{Log data to SD card:}
	Due to time constraints, it was not possible to implement this feature.
	\item[\xmark] \textbf{Transfer logs to monitoring station:}
	Since a log of the data is not kept, this requirement could not be fulfilled.
	\item[\cmark] \textbf{Start/stop transmission from nodes:}
	This feature is part of GoCAN, the protocol developed in the report.
	Commands can be issued to a node which will stop start and stop the transmission.
	This is shown in section \ref{sec:node_software}.
	\item[\cmark] \textbf{Present data to user:}
	A basic program reading the GPS data was written to act as a placeholder GUI.
	The output of this program is shown in section \ref{sec:frontendverification}.
	\item[\cmark] \textbf{Provide an API for data access:}
	A class was written to provide an API which acts as a front end to the underlying system.
	A function was written to interpret the GPS data and present it in a human readable format.
	This API was utilised in verifiying the previous requirement.
	\item[--] \textbf{Must continue to function on node failure:}
	This requirement is fulfilled only partially. 
	The network is agnostic to the number of nodes present at any one time and the failure of any sensor node will not bring the system down.
	The WiFi node does, however, provide the link between the CAN network and the monitoring station.
	Due to this, if the WiFi node fails, the system can no longer be used in monitoring data.
\end{itemize}

\subsection{Operational Requirements}
\begin{itemize}
	\item[\cmark] \textbf{A developer can add new nodes:}
	A framework has been created which allows the developer to add the necessary code to support nodes.
	Guidelines on how to implement new nodes are provided in appendix \ref{app:addnode}.
	\item[\cmark] \textbf{A developer can modify existing nodes:}
	Since the code for the framework mentioned in the previous requirement is available to the developer, it will also be possible to modify the code for any existing node.
	\item[\cmark] \textbf{A developer can add API for specific sensor:}
	The framework provides a front end class in which functions for accessing data from a particular node can be written.
	An outline of the process of adding to the API can be seen in appendix \ref{app:addnode}.
	\item[\cmark] \textbf{A developer can add custom (G)UI:}
	Since the API is readily available to the developers, the parameters can be accessed and utilised for any purpose, including creating a GUI.
	\item[\xmark] \textbf{A user can request a data log:}
	Since a log of the data is not kept, this feature was not implemented.
	\item[--] \textbf{A user can start/stop data transmission from nodes:}
	While toggling of transmission is implemented on a per node basis, there is no way for a user to issue this command through the API.
\end{itemize}

\subsection{Quality of Service Requirements}
\begin{itemize}
	\item[\cmark] \textbf{Can support up to 16 nodes:}
	GoCAN has a 4 bit node ID.
	This can uniquely identify up to 16 different node, of which one has to be the WiFi node.
	The distribution of the node ID's currently in use can be seen in section \ref{sub:CAN_protocol}.
	\item[\cmark] \textbf{Has wireless range greater than 80m:}
	A test was done to verify the range.
	It was found to be functional at a range of 110m.
	The test is described in section \ref{sec:wifiverification}.
	\item[\xmark] \textbf{CAN network has at least 1Mb/s data bandwidth:}
	With the CAN controller used, it was not possible to get the required data bandwidth.
	The actual data bandwidth was found to be 720 Kb/s.
	This calculation is presented in section \ref{sub:CAN_bandwidth}
	\item[\xmark] \textbf{Timestamps with a precision of 1 ms:}
	While timestamping is done, it is currently not possible to guarantee 1 ms precision.
	This is due to the node being run on an ordinary Linux system.
	If the data gathered on the network is to be useful in any data processing application, it is necessary to port the system to a real time platform.
\end{itemize}

\subsection{Design Requirements}
\begin{itemize}
	\item[\cmark] \textbf{Must allow for integration of new nodes:}
	The network is made such that it is agnostic with respect to the type and number of nodes on the network.
	This allows adding new nodes to the network without breaking existing nodes.
	Guidelines on how to implement new nodes are provided in appendix \ref{app:addnode}.
	\item[\cmark] \textbf{Software must be modular to allow for simple integration of nodes:}
	The software was created in such a way that as few files as possible need intervention from developers adding new nodes.
	This will help simplify the process and allow integration of new nodes with minimal knowledge of the underlying network.
	Guidelines on how to implement new nodes are provided in appendix \ref{app:addnode}.
\end{itemize}

