%!TEX root = ../main.tex
\label{sub:implementation_of_sensors}
This section will describe the implementation of the sensors selected during the analysis.
Of the three types of sensors, only the GPS was made to work.
\input{sections/interfacing_with_sevcon}


\subsection{Interfacing with the IMU}\label{sec:interface_IMU}
The used IMU is a VectorNav vn-100 IMU.
The physical interface to the IMU is a usb cable and when connected to Linux it shows up in \texttt{/dev/}.
VectorNav provides an extensive C an C++ library for both Windows and Linux use \cite{vectornav}. 
This library was used to confirm that the module functions as expected, however, due to time constraints, it was not used further.
\subsection{Interfacing with the GPS}\label{sec:interface_GPS}
The used GPS is a u-blox NEO-6P GPS module.
The physical interface to the GPS is a usb cable and the output adheres to the NMEA standard and is made of 8 different NMEA sentences.
The RMC sentence contains all essential information, that being position, velocity and time.
Therefore the implemented GPS class, that has the responsibility of interfacing the GPS, only needs to decode RMC sentences.
An example of a RMC sentence is shown in code \ref{code:rmc}.
The extracted information shows that the time is 09:11:23:00, the module is active, latitude is 55 degrees 22.03929 minutes North, longitude is 10 degrees 25.91037 minutes East, the speed is 0.348 knots, the date is  7th of November 2016 and checksum is 7C.
For the sake of simplicity all coordinates are converted to degrees with decimals. 
\begin{lstlisting}[caption=RMC sentence.,label=code:rmc]
$GPRMC,091123.00,A,5522.03929,N,01025.91037,E,0.348,,071116,,,
	A*7C
\end{lstlisting}

\subsubsection*{Service virtualization}
The GPS only produces interesting data when it receives data from a number of satellites. 
This means that the GPS antenna needs to be outside, which is not very practical when developing software.
Therefore the output from the GPS with the antenna outside was piped into a file.
This file was then read by a program with a fixed time interval thus making a service virtualization of the GPS.
This service virtualization was used when developing software for the GPS.