%!TEX root = ../main.tex

\section{On-vehicle Local Network}

\subsection{Topology}

There are various network topologies that can be used to setup the required node network for this project. These include the ring, bus, mesh ,star and tree topology. Before we specify which one is suitable, a brief description of the purpose of our network as well as an overview of their advantages and disadvantages are needed. 

\subsubsection{Purpose of the Network}
The purpose of this network is to accommodate multiple sensors which need to be able to communicate with the main node and the other present nodes. The reasons for this is that the main node is responsible for transmitting and receiving data from the stationary computer and other nodes may require data from other to cooperate for a task. The main node, apart from communicating, will also handle processing that the secondary nodes are not able to. The communication between the various nodes is preferred not to be strictly centralized. Two nodes may need to communicate with one another without the control and the extra processing time of a centralized topology. Furthermore, in case that one node fails, the network as a whole should still be operative. Lastly, since it is a multi-node network and it may require more nodes in the future, a certain level of scalability is also required.

\subsubsection{Different Topologies}
\begin{itemize}
\item \textbf{Bus:} This is the simplest, cheaper and easiest topology. All nodes communicate through a central bus and it is scalable with the addition of extra nodes on the two ends of the cable. The central bus introduces the risk of complete network failure in case of the bus failure and the decrease in performance in case of many nodes or heavy traffic.
\item \textbf{Ring:} All the nodes in this type of network form a ring, where each node is connected to its two neighbors. It has the advantages of the bus network as well, being cheap, simple and easy to implement. It shows better performance than the bus, even under heavy load. A centralized control is not required for this type and in case of a node failure, the ring breaks and it can continue to function as a bus network. It is scalable, but to a less extent than the bus. An alternative solution is the Dual Ring Topology, where a secondary cable is connected in parallel to the main cable, adding one more layer of reliability in case of failure of one of the two cables. This, in terms of required hardware, a total of four ports per node are needed.
\item \textbf{Mesh:} In this type, each node has direct connections to each other node present in the network. That provides speed and reliability in case of node failures, but requires more hardware and processing power to manage the connections. It is very robust but scalability is certainly not one of its features.
\item \textbf{Star:} The star topology is a centralized type of networking. All nodes are connected to a central hub, handling all the communication between them. It is fast, easy to implement and offers great reliability in case of node failures. The major disadvantage is that if the hub fails, the entire network fails. It can be scalable to a certain point, since the hub can be upgraded to handle more connections.
\item \textbf{Tree:} The last type, the tree is an extension of the bus and the star topologies combined. It can be easily scalable, but that adds extra difficulty in its maintenance. It also requires a lot of connections and in case the top (root) node fails, then all the network is down as well.
\item \textbf{Hybrid:} The last type is the hybrid one, where depending on the needs and purpose of the network, two or more topologies can be combined to achieve the best balance between their advantages and disadvantages.
\end{itemize}

\subsubsection{Suitable Topology}
Concluding from the above, the mesh type is not suitable, since it adds extra hardware requirements such as processing power and many redundant connections. A node may be a simple sensor with a small microprocessor and hence, connecting it to such a network is not feasible. Although the bus type may fit the requirements, the risk of failing due to a node malfunction can be high making it a secondary option. In our system, a small embedded board computer will handle the wireless communication, making it to be the important node that needs to keep its connection with the rest of the nodes even in case of failures. Apart from that, since this main node will also handle processing, it needs to be the central communicating node in all topologies that require a centralized node such as the star and the tree. Thus, the star topology is not suited, since in case of its failure, the whole network fails. Similarly, the tree is also not suited for the same reason. Scalability is also a requirement for the future connection of sensors or data producers. Although the majority of the types provide a level of scalability, the addition of extra nodes always decrease the overall performance of any network. Hence, a topology that balances the decrease in performance against the network's expansion is best suited for the project.\\\\
The approach that fits the requirements best is implementing a ring network, where each node may be a subnetwork of a different type depending on the needs, making it into a hybrid network having a ring topology as its basis. The ring type provides the best balance of reliability, scalability, hardware requirements and communication speed in comparison to the others.

\subsection{Networking technology}

Different networking technologies exist in use today, such as Ethernet, Can bus, CanOpen and Powerlink, among others. Can bus is widely used in the automotive industry with data rates up to 1Mbit/s for small networks lengths, but the classic Ethernet and Powerlink support data rates of at least 10Mbit/s. Furthermore, Powerlink is suitable for transmission of time-critical data and timing-synchronization of the nodes. 
\\\\
Since the Zybo board will be used possibly using PmodNIC100 modules as they are provided by the university, the openPowerlink protocol can be implemented in software using as hardware the existing Ethernet ports provided by the modules.





