%!TEX root = ../main.tex
\section{Introduction} % (fold)
\label{sec:system_analysis}
A thorough system analysis is needed in order to design a system that meets the needs expressed by the use cases. 
This section will present the analysis of the complete system, touching on the following topics:

\begin{itemize}
	\item  \textbf{Parameters of interest:} In order to create a well-suited system it is necessary to gain knowledge of the type of parameters that may be of interest to monitor.
	\item \textbf{Hardware for monitoring parameters:} Having a list of parameters, what hardware is necessary to collect and monitor these parameters.
	\item \textbf{Data rate:} An investigation of the amount of data that can be expected from data producers connected to the system is required.
	\item \textbf{Data collection:} A number of sensors and other data producers is expected to exist on the go-kart.
	It is necessary to analyse how data from these is collected most effectively.
	\item \textbf{Embedded platform:} An investigation of what requirements the platform running the go-kart part of the system should satisfy.
	\item \textbf{Wireless network:} Data is required to be transmitted wirelessly from the go-kart to the monitoring station.
	An investigation of the appropriate technology will be conducted.
	\item \textbf{Local storage:} In order to log data, some form of local storage is required.
	This investigation will examine what options exist on the available platform to choose the appropriate solution.
	\item \textbf{Monitoring station interface:} An analysis of the appropriate interface on the stationary part of the system will be conducted.
\end{itemize}

\input{sections/sensoranalysis}

\input{sections/datarateanalysis}

\input{sections/datacollectionanalysis}

\input{sections/canbusanalysis}

\input{sections/microcontrolleranalysis}

\input{sections/wirelessanalysis}

\input{sections/storageanalysis}

\section{Conclusion}
\label{sec:analysisconclusion}
\todo[inline]{This was changed. All of the bullets in the introduction to the analysis were addressed.}
In the analysis, a number of decisions were taken in order to give a preliminary idea of how the system should be implemented. \\

A number of parameters of interest were explored, eventually resulting in three types of sensors to be implemented, an IMU, a GPS and the motor controller.
These were the VN-100 from Vectornav, the NEO-6P from U-blox and the Sevcon Gen4, all of which were available from SDU.
Based on these sensors, the total data rate from the sensors was found to be 86.4Kb/s.
It was decided to make a distributed network of embedded platforms. 
CAN bus was selected to handle communication between these.\\

For implementation, the embedded platform has been selected to be the Zybo from Diligent, running Xillinux.
The wireless data connection between the go-kart and the stationary compute will be handled using WiFi.
The SD with Linux mounted in each Zybo had sufficient free storage for logging data at a high rate.
A Linux bases computer will be used to receive data wirelessly from the go-kart, and present it to a user. \\

These decisions resulted in a list of requirements, as seen in section~\ref{sec:system_requirements}.
A full overview of the system is displayed in figure~\ref{fig:complete_system}.
% section system_analysis (end)